---
title: "R_Code_Sample"
author: "Xinghuan Luo"
date: "6/21/2021"
output: pdf_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

I loaded required packages. 
```{r, results = "hide", message=FALSE}
pkg_list <- c("tidyverse", "assertthat", "here", "stargazer")
lapply(pkg_list, require, character.only = TRUE)
```

I created different folders to store different results. 
```{r}
folder_path <- c("data", "documentation", "proc", "results", "scripts", "latex")

for (folder in folder_path) {
  suppressWarnings(dir.create(here(folder)))
}

results_path <- c("figures", "tables") 

for (folder in results_path) {
  suppressWarnings(dir.create(here("results", folder)))
}

```

I imported two datasets, car_data and market_data. 
```{r cars}
initial_car_data<-
    list.files(path = here("data", "car_data"),
               pattern = "*.csv", 
               full.names = TRUE) %>% 
    map_df(~read_csv(., col_types = cols(.default = "c"))) 


initial_market_data<-
    list.files(path = here("data", "market_data"),
               pattern = "*.csv", 
               full.names = TRUE) %>% 
    map_df(~read_csv(., col_types = cols(.default = "c"))) 
```


I merged the two datasets together and fill in the missing values. 
```{r, results = "hide"}
initial_market_data <- initial_market_data %>% 
  mutate(ma_key = case_when(
    ma == "B" ~ "Belgium", 
    ma == "F" ~ "France", 
    ma == "G" ~ "Germany", 
    ma == "I" ~ "Italy", 
    ma == "U" ~ "UK"
    ), 
    ye = as.numeric(ye)
  )

initial_car_data <-  rename(initial_car_data, ma_key = ma) %>% 
  mutate(ye = as.numeric(ye) + 1900)

to_numeric <- c("li1", "li2", "li3", "li", "hp", "qu")
final_data <- inner_join(
  initial_car_data, 
  initial_market_data, 
  by = c("ma_key", "ye")
  ) %>% 
  mutate(
    across(
      all_of(to_numeric), 
      as.numeric)
  ) %>% 
  as_tibble()
  
nonmiss_avg <- function(data, miss_var, var1, var2, var_avg) {
  data %>% 
    mutate({{miss_var}} := if_else(is.na({{miss_var}}), 
                            3* {{var_avg}}-({{var1}} + {{var2}}), 
                            {{miss_var}}))
}

final_data <- final_data %>%   
  nonmiss_avg(li3, li1, li2, li) %>% 
  nonmiss_avg(li2, li3, li1, li) %>% 
  nonmiss_avg(li1, li3, li2, li) %>% 
  mutate(li = if_else(is.na(li), (li1 + li2 + li3)/3, li))  

non_missing <-  final_data %>% 
  filter(is.na(li1) | is.na(li2) |is.na(li3) | is.na(li)) %>% 
  nrow == 0
  
assert_that(non_missing)
```

I generated the variables for graph and regressions. 
```{r}
final_data_7090 <- final_data %>% 
  filter(ye == 1970 | ye == 1990) %>% 
  group_by(ye) %>% 
  mutate(decile = ntile(hp, 10)) %>% 
  group_by(ye, decile) %>% 
  mutate(li_mean = weighted.mean(li, qu), 
         mid_hp = median(hp), 
         li_mean = mean(li_mean), 
         ye = as.character(ye), 
         decile = as.numeric(decile),  
         log_hp = log(hp))

reg_70 = lm(li ~ hp + log_hp, weights = qu, data = subset(final_data_7090, ye == "1970"))
reg_90 = lm(li ~ hp + log_hp, weights = qu, data = subset(final_data_7090, ye == "1990"))

predicted_70 <- predict(reg_70, interval = "confidence") %>% 
  as_tibble()
predicted_90 <- predict(reg_90, interval = "confidence") %>% 
  as_tibble()

predicted_7090 <- bind_rows(predicted_70, predicted_90)

final_data_7090 <-  cbind(final_data_7090, predicted_7090) %>% 
  arrange(hp)

```

I generated the graphs. 
```{r}
ggplot(final_data_7090, aes(x = mid_hp, y = li_mean,  color = ye)) +
  geom_point() +
  geom_line(aes(x = hp , y = fit, color = ye), size = 1) +
  labs(title = "Relationship between Sales-Weighted Average of 
                \nFuel Consumption and Horsepower in 1970 and 1990", 
       x = "Horsepower Decile", 
       y = "Sales-Weighted Average of Fuel Consumption", 
       color = "Year") + 
  scale_x_continuous(breaks = seq(0, 120, 15)) + 
  theme(
    plot.title = element_text(hjust = 0.5), 
    panel.background = element_blank(), 
    axis.line = element_line(colour = "grey"), 
    legend.key = element_rect(fill = "white") , 
  ) 

ggsave("scatter_fitted.png", 
       width = 14, 
       height = 7, 
       path = here("results", "figures"))
```
The scatterplot plots the sales-weighted average of fuel consumption versus the midpointof each horsepower decile. The fitted curves regress fuel consumption on horsepower and log horsepower, using sales as sample weights. 


I generated the regression tables.
```{r, results = "hide"}
stargazer(reg_70, reg_90, 
          title = "Regression Results", 
          column.labels =  c("1970", "1990"), 
          column.separate = c(1, 1), 
          dep.var.labels = "Fuel Consumption", 
          covariate.labels = c("Horspower", "Log Horsepower"),
          omit.stat = c("adj.rsq", "res.dev"),
          df = FALSE, 
          colnames = FALSE, 
          model.numbers = FALSE, 
          out = here("results", "tables", "regression_results.tex")
  )

```


\begin{table}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{Fuel Consumption} \\ 
 & 1970 & 1990 \\ 
\hline \\[-1.8ex] 
 Horspower & 0.015 & 0.027$^{***}$ \\ 
  & (0.011) & (0.008) \\ 
  & & \\ 
 Log Horsepower & 2.908$^{***}$ & 0.947$^{**}$ \\ 
  & (0.407) & (0.422) \\ 
  & & \\ 
 Constant & $-$2.696$^{**}$ & 1.904 \\ 
  & (1.064) & (1.247) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 272 & 398 \\ 
R$^{2}$ & 0.753 & 0.658 \\ 
Residual Std. Error & 129.530 & 92.511 \\ 
F Statistic & 410.846$^{***}$ & 380.079$^{***}$ \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 





